### 2020-10-06 README.Rmd
Readme knit with SCBI
Small edits for clarity

* Plot posterior distributions of all parameters

@@

Because of the structure of the `bw_fit_model` object we cannot simply draw these curves based on the posterior distribution. `bw_fit_model` gives the parameteres *compared* to a baseline. This is often not of interest. So to display these parameters as we care about them we have to sample from the baseline distrubiton and from the comparison one to get the posterior distribution of interest.

@@

** SCBI

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("libe", "caca", "astr", "litu", "havi", "cagl", "cato")
)
```

>>>>

**Big Woods**

@@

Because of the structure of the `bw_fit_model` object we cannot simply draw these curves based on the posterior distribution. `bw_fit_model` gives the parameteres *compared* to a baseline. This is often not of interest. So to display these parameters as we care about them we have to sample from the baseline distribution and from the comparison one to get the posterior distribution of interest.

@@

**SCBI**

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("caca", "litu", "cagl", "cato")
)
```
